%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.0 (14/7/16)
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com) and Harsh (harsh.gadgil@gmail.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper]{twentysecondcv} % a4paper for A4
\usepackage[utf8]{inputenc}
\usepackage[portuguese]{babel}

% Command for printing skill overview bubbles
% Programming skill bars
\programming{{Microsoft Office $-$ LibreOffice $-$ G Suite / 5},  {Linux $-$ \LaTeX $-$  Raspberry Pi/ 4}, {Assembly $-$ SQL $-$  Python/ 2}, {Git $-$ Linux Server $-$ Confluence /4},{ADALM-PLUTO $-$ Freedom Board $-$ ARM / 3}, {Java $-$ C \slash C++ $-$ MATLAB \slash Octave / 4}, {VHDL $-$ TCL $-$ Shell Scripting / 4}, {Arduino $-$ 8051 $-$ 8086 / 3}, {Mentor Graphics $-$ Synopsys $-$ Eagle / 2}, {Xilinx Vivado $-$ Altera Quartus $-$ FPGA / 4}, {Electric VLSI $-$ Doxygen $-$ TaskJuggler / 4},{Cadence $-$ LTspice $-$ SpiceOpus / 4}}

\Languages{{Italian / 1}, {French / 1.3}, {English / 6}, {Portuguese (Native) / 6}}

%\uCuP{{Arduino $-$ 8051 $-$ 8086 / 3}, {Mentor Graphics $-$ Synopsys $-$ Fritzing / 3}, {Xilinx Vivado $-$ Altera Quartus $-$ FPGA / 4}, {Electric VLSI $-$ Doxygen $-$ TaskJuggler / 5},{Cadence $-$ LTspice $-$ SpiceOpus / 5}}


% Projects text
\education{
\textbf{Graduate Certificate, Embedded Systems}\\
University of Colorado - Boulder\\
2020 - Ongoing | Colorado, USA

\textbf{Beng, Electrical Engineering and Biomedical Engineering}\\
Exchange Programme - Science Without Borders \\
University of Glasgow \\
2014 - 2015 | Glasgow, Scotland

\textbf{BEng., Electrical Engineering} \\
University of Brasilia \\
2011 - 2019 | Brasília, Brazil
}

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------
% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\cvname{Guilherme \\Shimabuko} % Your name
\cvjobtitle{ Electrical Engineer } % Job
% title/career

\cvnumberphone{+55 61 9 9841-4243} % Phone number
\cvmail{gshimabuko@ieee.org} % Email address

%----------------------------------------------------------------------------------------

\begin{document}

\makeprofile % Print the sidebar
 
%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------
\section{About: }
\small{Electrical Engineer with strong interest in Electronics and Computer Systems. Open Source and Open Hardware Enthusiast with long term experience in several Linux distributions. Proactive, team-player, and with experience in management and team training.}

\section{Relevant Experience}
\begin{twenty} % Environment for a list with descriptions
\twentyitem
    	{LPCI - Department of Electrical Engineering - UnB}
		{Research Assistant \hfill \textit{January, 2020 - Currently}\\}
        {Intern \hfill\textit{November, 2018 - December, 2019}}
        {\textit{November, 2018 - December, 2019}}
        {
            \color{pblue}{\hspace{8pt}-\hspace{4pt}} \color{black}\textbf{Digital Systems: }Digital circuits design and validation on FPGA and ASIC for satellite communications using Cadence IC Design Framework.
            
            \color{pblue}{\hspace{8pt}-\hspace{4pt}} \color{black}\textbf{IT Management: }Validation and maintenance of project tools. Linux Server management, as well as client support (Ubuntu, CentOS, ArchLinux).
            
            \color{pblue}{\hspace{8pt}-\hspace{4pt}} \color{black}\textbf{Human Resources: }Team recruiting and training in order to assemble an integrated circuits design team.
            
            \color{pblue}{\hspace{8pt}-\hspace{4pt}} \color{black}\textbf{Project Management: }Project planning and tracking. Activity log system implementation. Project Documentation. Implementation, optimization and automation of design flow.
        }
        \\
	\twentyitem
    	{DFchip}
		{Intern}
        {November, 2015 - January, 2017}
        {
            \color{pblue}{\hspace{8pt}-\hspace{4pt}} \color{black}{\textbf{Digital Systems: }Digital circuits design and validation on FPGA, ASIC, and SoC, as well as the implementation and documentation of Digital Systems design flow using Cadence IC Design Framework.}
            
            \color{pblue}{\hspace{8pt}-\hspace{4pt}} \color{black}{\textbf{Analogue Systems: }Training in Analog Circuit Design using Cadence IC Design Framework.}
            
            \color{pblue}{\hspace{8pt}-\hspace{4pt}} \color{black}{\textbf{IT Management: }Validation and maintenance of Design Flow Tools in Linux Clients (OpenSUSE).}
        }
        \\
    \twentyitem
    	{Medialab 
